On Adding Pattern Matching to Haskell-based Deeply Embedded Domain Specific Languages\\ \large{Not For Distribution}

### 2020-07-21 paper/paper.tex
Some small changes in the abstract

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
% Say what problem is
  Capturing control flow is the Achilles heel of Haskell-based
  deeply embedding Domain Specific Languages,
  clunkly workarounds must be employed which will be less familiar
  than the builtin control flow mechanisms of the host language.  
% Say why it is an interesting problem
  However, capturing control flow in an embedded domain specific language is crucial for
  writing programs in a natural style, and enables the programmer to use the
  constructs that are already builtin to the base language, such as pattern
  matching and recursion.
% Say what our solution achieves
  In this paper, we expand the capabilies of traditional,
  Haskell-based, deep embeddings with a compiler extension
  for reifying conditionals and pattern matching.
% Here is why the world will be a better place
  With this new support, the Haskell that we capture for expressing
  deeply embedded domain specific languges can be cleaner, more Haskell idiomatic,
  and more declarative in nature.

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
% Say what problem is
  Capturing control flow is the Achilles heel of Haskell-based
  deeply embedded domain specific languages. Clunky, awkward workarounds must be
  employed which will be less familiar than the builtin control flow mechanisms
  of the host language.

% Say why it is an interesting problem
  However, capturing control flow in an embedded domain specific language is crucial for
  writing programs in a natural style, and enables the programmer to use the
  constructs that are already builtin to the base language, such as pattern
  matching and recursion.
% Say what our solution achieves

  In this paper, we expand the capabilities of traditional,
  Haskell-based, deep embeddings with a compiler extension
  for reifying conditionals and pattern matching.
% Here is why the world will be a better place
  With this new support, the Haskell that we capture for expressing
  deeply embedded domain specific languages can be cleaner, more Haskell idiomatic,
  and more declarative in nature.
